---
author: Sarah Zeller
title: Homework assignment 1
subtitle: Predicting mobile coverage years in Tanzania
format:
  html: 
    toc: true
    mainfont: "Open Sans"
  pdf:
    toc: true
    number-sections: true
    mainfont: "Open Sans"
    include-in-header: 
      - text: |
          % für Alignment bei Kommastelle
          \usepackage{booktabs}
          \usepackage{siunitx}
          % alle Tabellen kleiner setzen
          \usepackage{etoolbox}
          \AtBeginEnvironment{longtable}{\footnotesize}
          \AtBeginEnvironment{tabular}{\footnotesize}
          \sisetup{group-separator       = {,}, % default: \, ("thinspace")
                  group-minimum-digits  = 3,   % default: 5
                  input-decimal-markers = {.}} % default: "{.,}"
execute:
  warning: false
  echo: false
bibliography: references.bib
editor: 
  markdown: 
    wrap: sentence
---

{{< pagebreak >}}

In this report, I'm having a look at cell phone towers in Tanzania, and estimate when they are built.

```{r}
#| label: install-packages
#| echo: false
#| output: false
#| warning: false

install.packages("renv", quiet = TRUE)
renv::hydrate()
install.packages("remotes", quiet = TRUE)
remotes::install_github("ropensci/rnaturalearthhires")
```

```{r}
#| label: load-packages
library(here)
library(archive)
library(sf)
library(mapview)
library(ggtext)
library(tidyverse)
library(rnaturalearth)
library(rnaturalearthhires)
library(osmdata)
library(nngeo)
library(modelsummary)
library(kableExtra)
library(labelled)
library(fixest)

library(showtext)
font_add_google("Open Sans")
showtext_auto()


here("run_regressions.R") |> source()
here("show_regressions.R") |> source()
st_erase <- function(x, y) st_difference(x, st_union(st_combine(y)))

crs_africa <- "ESRI:102022"
```

```{r}
#| label: check-for-output-folder
if (!"output" %in% (here() |> list.files())) {
  here("output") |> dir.create()
}
```

# Project region

Before diving into the details, let's have a look at the region I am talking about.
@fig-locator-map shows where in the world our country of interest lies, while @fig-basemap shows some political details.
Tanzania lies in Eastern Africa, with its coast towards the Indian Ocean.
It is divided into 30 states.
Most importantly, I can see Tanzania's borders and the coast line.
I will include both in the later regression analysis.
Possibly, countries decide to build cell phone towers further away from the border because neighboring countries may already provide the infrastructure.
Close to the coastline, it is also possible that the terrain is more even or that other infrastructure is already laid out; this may make it easier to build cell phone towers.
Also, tourism may be more important close to the coast, which may drive an early pressure to build cell phone towers.

```{r}
#| label: load-tanzania

tanzania_whole <- ne_countries(country = "United Republic of Tanzania",
                               scale = 10,
                               returnclass = "sf") |> 
  st_transform(crs = crs_africa)

tanzania <- ne_states(country = "United Republic of Tanzania",
                      returnclass = "sf") |> 
  st_transform(crs = crs_africa)

coast <- tanzania_whole |> 
  st_transform(crs = 4326) |> 
  st_buffer(10) |> 
  st_intersection(ne_coastline(scale = 10,
                               returnclass = "sf")) |> 
    st_transform(crs = crs_africa)

islands <- tanzania_whole |> 
  st_cast('MULTILINESTRING') |> 
  st_cast('LINESTRING', do_split = TRUE) %>%
  `[`(2:7,) # select islands

borders <- tanzania_whole |> 
  st_cast('MULTILINESTRING') |> 
  st_cast('LINESTRING', do_split = TRUE) %>%
  `[`(1,) |> # select mainland
  st_erase(coast |> st_buffer(1)) # buffer slightly to create overlap

```

```{r}
#| label: fig-locator-map
#| fig-cap: Research area is located in Tanzania.

world <- ne_countries(scale = "small",
                      returnclass = "sf") |> 
  st_cast('MULTILINESTRING') |> 
  st_cast('LINESTRING', do_split = TRUE) |> 
  mutate(npts = npts(geometry, by_feature = TRUE)) |> 
  st_cast('POLYGON')

ggplot() +
  geom_sf(data = world,
          aes(fill = sovereignt == "United Republic of Tanzania")) +
  scale_fill_manual(values = c("grey90",
                               "#1EB53A")) +
  guides(fill = FALSE) +
  coord_sf(crs = "+proj=ortho +lat_0=5 +lon_0=-10") +
  labs(caption = "Data: Natural Earth") +
  theme_void() +
  theme(text = element_text(family = "Open Sans"))

```

```{r}
#| label: fig-basemap
#| fig-cap: Political map of Tanzania

africa <- ne_countries(continent = "africa",
                       scale = 10,
                       returnclass = "sf") |> 
  st_transform(crs = crs_africa)

bounds <- tanzania_whole |> 
  st_buffer(100000) |> 
  st_bbox()

basemap <- 
  ggplot() +
  geom_sf(data = africa,
          fill = "grey90",
          col = "grey80") +
  geom_sf(data = tanzania,
          fill = "white",
          col = "grey70") +
  coord_sf(xlim = c(bounds$xlim, bounds$xmax),
           ylim = c(bounds$ylim, bounds$ymax),
           crs = crs_africa) +
  annotate("text",
           label = "Indian \nOcean",
           x = 1650000,
           y = -1100000,
           size = 2.5,
           lineheight = .75,
           colour = "grey40") +
  theme_void() +
  theme(panel.background = element_rect(fill = alpha("cornflowerblue", .4),
                                        colour = NA),
        text = element_text(family = "Open Sans")) +
  labs(caption = "Data: Natural Earth")

basemap
```

# Data

## Antennas in Tanzania

Our focus in this report is on cell phone antennas in Tanzania.
Therefore, let's have a look at where cell phone towers were built until end of 2022.
I only consider on antennas that fall within the boundaries of one of Tanzania's states.
Data come from Open Cell ID. @fig-map-cellid shows when antennas were built for three different technologies:

-   GSM (aka 2G)
-   UMTS (aka 3G)
-   LTE (aka 4G)

We can see that LTE antennas only started being built recently.
The islands appear to be rather newly connected as well.
Also, the pattern of both GSM and UMTS antennas indicates a line along which many of them were built; this may be a road or similar infrastructure.
Large areas of land in the West and South East are not covered by any antennas so far.

```{r}
#| label: load-cellid
here("input/opencellid_tanzania.RData") |> load()

open_cell <- opencellid_tanzania |> 
  # convert to sf and project to Africa equal area projection
  st_as_sf(coords = c("lon", "lat"),
           crs = 4326) |> 
  st_transform(crs = crs_africa) |> 
  filter(created_year <= 2022) |> # complete years
  mutate(across(c(created, updated), as_datetime)) |> 
  mutate(created_year = year(created) |> as.integer(),
         create_month = month(created)) |> 
  # order 2G/3G/4G
  mutate(radio = factor(radio, 
                        levels = c("GSM", "UMTS", "LTE"), 
                        ordered = TRUE))|> 
  # add state and subset for only antennas within known states
  st_intersection(tanzania |> transmute(state = name)) 


```

```{r}
#| label: fig-map-cellid
#| fig-cap: Cell phone towers in Tanzania

basemap + 
  geom_sf(data = open_cell |> st_jitter(), 
          aes(col = created_year),
          size = .1) +
  facet_wrap(~radio) +
  # have to set this again after facet_wrap
  coord_sf(xlim = c(bounds$xlim, bounds$xmax),
           ylim = c(bounds$ylim, bounds$ymax)) +
  labs(caption = "Data: OpencellID",
       col = "Construction year") +
  theme(legend.position = "bottom",
        legend.key.width = unit(1, "cm"),
        legend.margin = margin(t = 1),
        text = element_text(family = "Open Sans"))
```

## Road data

In @fig-map-cellid, we could discern some patterns that seemed like roads or railways.
I therefore have a look at road and railway data.
However, I focus on roads that are paved.
This is because it seems likely that more robust infrastructure is needed to install the necessary cables to connect antennas to the internet.
I expect paved roads to be centrally planned by government, with thoughts to such developments, where it should be easier to install cables.
Road data are from GRIP: global roads database.

@fig-map-roads shows the paved road network in Tanzania.
There is a dense spot on the Northern coast: Dar es Salaam, the most populous city.
Besides that, there are some regional clusters where more roads are paved, and some longer roads connect the whole country.
The same pattern as with the antennas appears: in the West and South East, the road network is less dense.
It is also noticeable that a lot of roads lead to borders.
For the islands, on the other hand, there are at least no data on paved roads.

```{r}
#| label: download-data-roads
if (!"roads.zip" %in% (here("output") |> list.files())) {
  # reset timeout for download to longer time
  old_timeout <- getOption('timeout')
  options(timeout = 200)
  # download
  download.file("https://dataportaal.pbl.nl/downloads/GRIP4/GRIP4_Region3_vector_shp.zip",
                here("output/roads.zip"))
  # set back to before
  options(timeout = old_timeout)
  # extract
  archive_extract(here("output/roads.zip"),
                  "output/roads/")
}

```

```{r}
#| label: load-roads

roads <- here("output/roads/GRIP4_region3.shp") |> 
  read_sf() |> 
  # pre-filter for Southern Africa
  filter(GP_RRG == 10) |> 
  st_transform(crs = crs_africa) |> 
  # make sure it's limited to Tanzania
  st_intersection(tanzania_whole)

paved_roads <- roads |> 
  # filter for paved roads
  mutate(GP_RSE == 1) 

```

```{r}
#| label: fig-map-roads
#| fig-cap: Paved roads in Tanzania
basemap +
  geom_sf(data = paved_roads) +
    coord_sf(xlim = c(bounds$xlim, bounds$xmax),
           ylim = c(bounds$ylim, bounds$ymax)) +
  labs(caption = "Data: Global Road Inventory Project") +
  theme(text = element_text(family = "Open Sans"))
```

## Train data

After having a look at the road network, I examine a more historical network: the railways.
These date back to the late 19th century and cover less ground than the road network.
Train data are from Humanitarian OpenStreetMap Team.
@fig-map-trains shows the railroad network.
It connects the West with the coast; all lines end in on point, probably Dar es Salaam with its harbour.

```{r}
if(!"trains.zip" %in% (here("output") |> list.files())) {
  # download
  download.file("https://export.hotosm.org/downloads/c5cc333b-1bfa-4621-b521-273206860c0b/hotosm_tza_railways_lines_shp.zip",
                here("output/trains.zip"))
  # extract
  archive_extract(here("output/trains.zip"),
                  "output/trains/")
}
```

```{r}
#| label: load-trains
trains <- here("output/trains/hotosm_tza_railways_lines.shp") |> 
  read_sf() |> 
  st_transform(crs = crs_africa)
```

```{r}
#| label: fig-map-trains
#| fig-cap: Railroads

basemap + 
  geom_sf(data = trains) +
  coord_sf(xlim = c(bounds$xlim, bounds$xmax),
           ylim = c(bounds$ylim, bounds$ymax)) +
  labs(caption = "Data: Open Street Maps") +
  theme(text = element_text(family = "Open Sans"))
```

## City data

Additionally to infrastructure, population is important.
Where there are people, there is an increased need for cell phone reception.
While there are also applications for agriculture, it would seem more urgent to prioritize more voters during the first roll-out.
@fig-map-cities shows cities in Tanzania; data come from the `maps` package in R.
A similar pattern as before emerges: the West and South East are not as densely populated.
While Dodoma is the capital, it only has a quarter of the population of the largest Tanzanian city, Dar es Salaam.
It may thus be prudent to include both cities in the analysis.

```{r}
#| label: load-cities

library(maps)
data("world.cities")

cities <- world.cities |> 
  filter(country.etc == "Tanzania") |> 
  # set capital as boolean
  mutate(capital = capital == 1,
         size = case_when(pop > 2e6 ~ "> 2 million",
                          pop > 1e5 & pop < 2e6 ~ "> 100,000",
                          pop <= 1e5 ~ "< 100,000")) |> 
  st_as_sf(coords = c("long", "lat"),
           crs = 4326) |> 
  st_transform(crs = crs_africa)
```

```{r}
#| label: fig-map-cities
#| fig-cap: Cities in Tanzania

basemap + 
  geom_sf(data = cities,
          aes(size = size,
              col = capital | name == "Dar es Salaam"),
          alpha = .5) +
  coord_sf(xlim = c(bounds$xlim, bounds$xmax),
           ylim = c(bounds$ylim, bounds$ymax)) +
  scale_colour_manual(values = c("grey40",
                                 "darkred")) +
  annotate("text",
           label = c("Dodoma",
                   "Dar es \nSalaam"),
           col = "darkred",
           size = 2.5,
           lineheight = 1,
           x = c(1130000,
                 1585350),
           y = c(-700000,
                 -700799)) +
  guides(col = FALSE) +
  labs(caption = "Data: {maps} library",
         size = "Population") +
  theme(text = element_text(family = "Open Sans"))

```

## Point of worship

Points of worship are any infrastructure where people worship -- e.g. mosques or churches.
For the point of worship, I use data from OSM.
I download it through the `osmdata` R package [@osmdata].
While I use Tanzania's bounding box to download data, I later intersect it with Tanzania's shape to only retain points of worship within the country borders.
The dataset provides point, line and polygon features.
I only use point features, since these are the most frequent.

```{r}
#| label: load-pofw

if (!"pofw.rds" %in% (here("output") |> list.files())) {
  pofw <-
    getbb("Tanzania", featuretype = "country") |>
    opq(timeout = 100) |>
    add_osm_feature(key = "amenity",
                    value = "place_of_worship") |>
    osmdata_sf() %>%
    # filter out point layer
    `[[`(4) |>
    # intersect with tanzania to only get Tanzanian pofw
    st_transform(crs = crs_africa) |>
    st_intersection(tanzania_whole)
  pofw |> 
    saveRDS(here("output/pofw.rds"))
} else
  pofw <- here("output/pofw.rds") |> readRDS()
```

```{r}
#| label: fig-pofw
#| fig-cap: Points of worship

basemap +
  geom_sf(data = pofw,
          alpha = .5) +
  coord_sf(xlim = c(bounds$xlim, bounds$xmax),
           ylim = c(bounds$ylim, bounds$ymax),
           crs = crs_africa) +
  labs(caption = "Data: Open Street Maps")

```

@fig-pofw shows the points of worship within Tanzania.
Little surprisingly, a similar image as with the other variables emerges: the points of worship are in the same areas as cities, i.e. where people live.
However, these data are more detailed and may show city centers, or areas where there is still room for building new infrastructure.
They also show areas where the local population has enough income to build points of worship.

## Lightning frequency

Lightning frequency may influence whether an antenna is built: it makes it more difficult for technicians to set them up.
This frequency has also been used as an instrument for mobile internet antennas in recent papers.
I obtained the data from (NASA)[https://ghrc.nsstc.nasa.gov/lightning/] and already pre-cleaned the lightning dataset for another project, so here, I will use the cleaned dataset.
It contains the lightning frequency for 50x50 $km^2$ raster areas, as an average of all days in 2014.
I intersect this dataset with Tanzania to retain only the areas of interest.
The dataset also includes a raster ID for each raster.

```{r}
#| label: load-lightning

if (!"lightning.rds" %in% (here("output") |> list.files())) {
  lightning <- here("input/lightnings_2014.rds") |> 
    readRDS() |> 
    st_transform(crs = crs_africa) |> 
    st_intersection(tanzania_whole$geometry)
  lightning |> 
    saveRDS(here("output/lightning.rds"))
} else
  lightning <- here("output/lightning.rds") |> readRDS()
```

```{r}
#| label: fig-lightning
#| fig-cap: Lightning frequencies

basemap +
  geom_sf(data = lightning,
          aes(fill = lightnings_mean_2014)) +
  coord_sf(xlim = c(bounds$xlim, bounds$xmax),
           ylim = c(bounds$ylim, bounds$ymax)) +
  labs(caption = "Data: NASA",
       fill = "Average lightning \nfrequency (2014)")
```


## Calculating distances

Now that I have described all variables, I calculate the distance from cell phone towers to the (nearest)

-   road
-   railway
-   coast
-   border
-   capital
-   point of worship.

To calculate the distances correctly, I first project the geometries to the *WGS 1984 Albers for Africa* equal area projection (ESRI:102022).
Then, I use the `nngeo` [@nngeo] package, and its function `st_nn`.
For each cell phone tower, it calculates the distance to the nearest neighbour.
Instead of receiving a matrix, I simply get a list with two vectors.
The first vector includes the index for the nearest neighbour for each cell phone tower.
The second vector includes the distance to this nearest neighbour.
I do this for each variable of interest.
When merging those distances with the Open Cell ID data, I transform them into kilometers.

Additionally, I determine whether a cell phone toIr is on an island.
In this case, I still determine the distance to the coast; but I set the distance to the border to the mean value of the mainland distances.
This is because I do not have the precise outline of the border in the ocean.
I consequently add an island dummy to the analysis.

Lastly, I add the lightning frequency for the area in which each antenna lies.
I do this by simply intersecting the lightning frequency polygons with the antenna points.

@tbl-summary-vars shows the descriptive statistics for these variables.
We can see that all variables have the same number of observations, implying that we have all variables for all antennas.
For all variables, there is quite a range, and most are left-skewed.


```{r}
#| label: calculate-dist-road

# calculate distance to nearest neighbor road
if (here("output/nn_paved_roads.rds") |> file.exists()) {
  nn_paved_roads <- readRDS("output/nn_paved_roads.rds")
} else {
  nn_paved_roads <- st_nn(open_cell,
                          paved_roads,
                          returnDist = TRUE)
  saveRDS(nn_paved_roads,
          "output/nn_paved_roads.rds")

}
# extract distances
dists_roads <- sapply(nn_paved_roads[[2]], "[", 1)
```

```{r}
#| label: calculate-dist-train

# calculate distance to nearest neighbor railway
if (here("output/nn_trains.rds") |> file.exists()) {
  nn_trains <- readRDS("output/nn_trains.rds")
} else {
  nn_trains <- st_nn(open_cell,
                          trains,
                          returnDist = TRUE)
  saveRDS(nn_trains,
          "output/nn_trains.rds")

}
# extract distances
dists_trains <- sapply(nn_trains[[2]], "[", 1)
```

```{r}
#| label: calculate-dist-coast

# calculate distance to coast
if (here("output/nn_coast.rds") |> file.exists()) {
  nn_coast <- readRDS("output/nn_coast.rds")
} else {
  nn_coast <- st_nn(open_cell,
                          coast,
                          returnDist = TRUE)
  saveRDS(nn_coast,
          "output/nn_coast.rds")
}
# extract distances
dists_coast <- sapply(nn_coast[[2]], "[", 1)

```

```{r}
#| label: calculate-distance-borders

# calculate distance to border
if (here("output/nn_border.rds") |> file.exists()) {
  nn_border <- readRDS("output/nn_border.rds")
} else {
  nn_border <- st_nn(open_cell,
                     tanzania_whole,
                     returnDist = TRUE)
  saveRDS(nn_border,
          "output/nn_border.rds")
}
# extract distances
dists_border <- sapply(nn_border[[2]], "[", 1)
```

```{r}
#| label: check-if-on-island

if (here("output/on_island.rds") |> file.exists()) {
  on_island <- readRDS("output/on_island.rds")
} else {
  on_island <- st_intersects(open_cell,
                             islands |> st_buffer(10000))
  saveRDS(on_island,
          "output/on_island.rds")
}
# extract distances
is_on_island <- on_island %>% lengths > 0

```

```{r}
#| label: calculate-distance-capital

# calculate distance to capital
if (here("output/nn_capital.rds") |> file.exists()) {
  nn_capital <- readRDS("output/nn_capital.rds")
} else {
  nn_capital <- st_nn(open_cell,
                      # Dodoma location
                      cities |> filter(name == "Dodoma"),
                      returnDist = TRUE)
  saveRDS(nn_capital,
          "output/nn_capital.rds")
}
# extract distances
dists_capital <- sapply(nn_capital[[2]], "[", 1)

```

```{r}
#| label: calculate-distance-pofw

# calculate distance to nearest point of worship
if (here("output/nn_pofw.rds") |> file.exists()) {
  nn_pofw <- readRDS("output/nn_pofw.rds")
} else {
  nn_pofw <- st_nn(open_cell,
                   pofw,
                   returnDist = TRUE)
  saveRDS(nn_pofw,
          "output/nn_pofw.rds")
}
# extract distances
dists_pofw <- sapply(nn_pofw[[2]], "[", 1)

```
```{r}
#| label: get-lightning-frequency

if (here("output/mobile_lightning.rds") |> file.exists()) {
  mobile_lightning <- readRDS("output/mobile_lightning.rds")
} else {
  lightning_overlaps <- st_intersects(open_cell,
                                      lightning)
  
  # check that all have an overlap
  assertthat::assert_that(all(lightning_overlaps %>% lengths > 1))

  # prepare lightning index and data frame
  lightning_index <- sapply(lightning_overlaps, `[[`, 1)

  lightning_wo_geometry <- lightning |> 
    as.data.frame() |> 
    select(-geometry)

  # merge
  mobile_lightning <- open_cell |> 
    cbind(lightning_wo_geometry[lightning_index,])
  
  # check that all antennas have a lightning value
  assertthat::assert_that(all(
    !is.na(mobile_lightning$lightnings_mean_2014)
    ))
  
  saveRDS(mobile_lightning,
          "output/mobile_lightning.rds")
}
```


```{r}
#| label: merge-dist-w-opencell
# merge into open_cell data frame
open_cell_w_distances <- mobile_lightning |> 
  mutate(state_id = state |> as.factor() |> as.integer()) |> 
  rename(lightning = lightnings_mean_2014) |> 
  # prettify labels
  mutate(state = labelled(state, 
                          label = "State"),
         lightning = labelled(lightning,
                              label = "Mean lightning frequency (2014)")) |> 
  mutate(dist_road_km = labelled(dists_roads / 1000, 
                                 label = "Distance to road (km)"),
         dist_train_km = labelled(dists_trains / 1000, 
                                  label = "Distance to railway (km)"),
         dist_border_km = labelled(dists_coast / 1000, 
                                   label = "Distance to border (km)"),
         dist_coast_km = labelled(dists_coast / 1000, 
                                  label = "Distance to coast (km)"),
         on_island = labelled(is_on_island |> as.integer(),
                              label = "Island position"),
         dist_capital_km = labelled(dists_capital / 1000, 
                                    label = "Distance to capital (km)"),
         dist_pofw_km = labelled(dists_pofw / 1000,
                                 label = "Distance to point \nof worship (km)")) |> 
  # account for islands
  mutate(dist_border_km = ifelse(is_on_island, NA, dist_border_km)) 

fill_value <- open_cell_w_distances$dist_border_km |> mean(na.rm = TRUE)

open_cell_w_distances <- open_cell_w_distances |>
  mutate(dist_border_km = ifelse(is_on_island, fill_value, dist_border_km) |> 
           labelled(label = "Distance to border (km)"))

saveRDS(open_cell_w_distances,
        here("output/open_cell_w_distances.rds"))
```

```{r}
#| label: tbl-summary-vars
#| tbl-cap: Distance summaries

selected_cols <- open_cell_w_distances |>
  as.data.frame() |>  # take out geometry
  select(starts_with(c("dist_",
                       "on_",
                       "lightning"))) |>
  names()

# prepare histogram sparklines
tmp_list <- open_cell_w_distances |> 
  as.data.frame() |> 
  select(all_of(selected_cols)) |>
  lapply(na.omit) |> 
  lapply(scale)

# formatting things
emptycol <- function(x) " "
f <- function(x) format(round(x, 2), big.mark=",")
# formula
formula_summary <- paste(
  paste(paste0(selected_cols), collapse = "+"), 
  '~ N + Mean + SD + Median + Min + Max + Heading("Histogram") * emptycol')

datasummary(formula = as.formula(formula_summary),
            data = open_cell_w_distances,
            format = f,
            output = "data.frame") |> 
  kbl(booktabs = TRUE,
      align = c("l", rep("r", 6), "c")) |> 
  column_spec(column = 8, image = spec_hist(tmp_list))

```

# Regression results

In the next step, I want to analyze what determines the timing of antenna construction.
I do this separately for each technology: GSM, UMTS and LTE.
I use the `fixest` package [@fixest] to run regressions with the amassed data set.
I then use the `modelsummary` [@modelsummary] package to show the regression output.

I run the following specifications:

(1) baseline OLS
(2) OLS with fixed effects (FE-OLS) on state-level and state-level clustered standard errors
(3) (2) with heteroskedasticity-robust standard errors (White correction)
(4) FE-OLS on raster-id level and with raster-level clustered standard errors (excluding the lightning variable, since it is colinear with the raster-id)
(5) FE-OLS with Conley standard errors




```{r}
#| label: run-regressions

formula <- reformulate(selected_cols,
                       "created_year")


gsm_list <- open_cell_w_distances |> 
  filter(radio == "GSM") |> 
  run_regressions(formula = formula)

umts_list <- open_cell_w_distances |> 
  filter(radio == "UMTS") |> 
  run_regressions(formula = formula)

lte_list <- open_cell_w_distances |> 
  filter(radio == "LTE") |> 
  run_regressions(formula = formula)

```
## GSM
@tbl-summary-gsm shows the regression results for the oldest technology: GSM.
Overall, the explanatory power of the models is modest ($R^2 \approx 0.2$).
However, it does increase when including FE; and more when the states are controlled for than if the raster IDs are controlled for.
The only variable that is robust to all specifications is the distance to the next point of worship. 
If it increases by $1km$, the building point of time for an antenna increases by $365 * 0.15 \approx 55$ days.
The mean lightning frequency is also mostly robust, with a large positive and highly significant effect.
If the mean lightning frequency increases from 0 to the maximum lightning frequency measured (0.00029), building an antenna is pushed back by approximately 9 months.

All other effects are not robust, so I do not discuss them further.

```{r}
#| label: tbl-summary-gsm
#| tbl-cap: Determinants of building a GSM antenna

show_regressions(gsm_list)

```

## UMTS

@tbl-summary-umts shows the regression results for the UMTS technology.
The explanatory power is similar to the model for GSM technology: about 20% of variation are explained.
Results are very similar to the GSM technology: distance to point of worship is highly significant and robust.
It pushes the timing of building an antenna back.
The same goes for the mean lightning frequency, which is also highly significant and robust.
All other distances are not significant/robust.

```{r}
#| label: tbl-summary-umts
#| tbl-cap: Determinants of building a UMTS antenna

show_regressions(umts_list)

```

## LTE
@tbl-summary-lte shows the regression results for the most recent antennas with LTE technology.
Here, the results differ from the other two technologies.
Firstly, the explanatory power is much higher ($R^2 \approx 0.5$).
Also, the FE do not add much explanatory power.
Interestingly, the distance to the next point of worship is not significant anymore.
Instead, the distance to railways and to the borders becomes more important: while antennas closer to railways are built later, they are built sooner when they are closer to the border.

Again, the mean lightning frequency in 2014 is significant and robust, but the effect is less pronounced than with the other two technologies.

```{r}
#| label: tbl-summary-lte
#| tbl-cap: Determinants of building a LTE antenna

show_regressions(lte_list)

```

# Discussion and conclusion

In this report, I analyzed determinants of the timing of building cell phone antennas in Tanzania.
The mean lightning frequency appears to be a strong predictor, which is highly significant and robust to changing model specifications.
This is little surprising, since it is used as an instrument in literature.

It appears that the predictors vary from the old technology (GSM/2G and UMTS/3G) to the new (LTE/3G): the most important distance predictor changes from point of worship to railway.

One interpretation is that with the older antennas, the focus was on reaching as many people as possible. 
Where there are points of worship, there are more people.
In more recent years, maybe more areas were already covered, so areas which are less densely populated may have been covered as well.
This would explain why distance to railway is important: the closer an antenna point is to the railway, the sooner the antenna will be built.
This could be because in less densely populated areas, already existing infrastructure, i.e. railways, are used heavily as a backbone for the new infrastructure, i.e. antennas.

{{< pagebreak >}}

# References {.unnumbered}
